\LARGE \bf A Hybrid Control Design for Autonomous Vehicles at Uncontrolled Intersections

### 2019-02-13 conference/iv2019/manuscript.tex
converting last two chapters of thesis into journal paper

\author{Nitin R. Kapania$^{1}$, Vijay Govindarajan$^{2}$, Francesco Borrelli$^{2}$% <-this % stops a space
\thanks{*This work was supported by the Hyundai Center of Excellence}% <-this % stops a space
\thanks{$^{1}$Dept. of Mechanical Engineering, Stanford University. Nitin Kapania is also a visiting scholar at UC Berkeley.}%
\thanks{$^{2}$Dept. of Mechanical Engineering, UC Berkeley.}%
}

@@

&\\
 2. Efficiency & a. Average speed: Minimize \\ 
        & deviation from speed of traffic \\  
        & b. Wait for pedestrian crossing \\
        & event to materialize before yielding. \\

        & \\
 3. Smoothness & a. Low acceleration: Nominal brake \\ 
 			  & and acceleration limits of 2 $\mathrm{m/s^2}$ \\

@@

\If {$state = HARD\hspace{1 mm}BRAKING$}
	\State $v_{des} = \mathrm{getDesiredSpeed}(d, v)$
	\State $a = -\frac{v^2}{2d} + k_s(v - v_{des})$ 	
	\If {$\textbf{not} \hspace{1 mm} \mathrm{inCrosswalk}(x_p)$} \State $state \leftarrow DRIVING$

@@

\EndIf
\If {$state = SPEED\hspace{1mm}UP$}
	\State $a = a_\mathrm{cmf}$ 	
	\If {$\textbf{not} \hspace{1mm} \mathrm{inCrosswalk}(x_p) \vee d < 0$} \State $state \leftarrow DRIVING$

>>>>

\author{Nitin R. Kapania$^{1}$, Vijay Govindarajan$^{2}$, Francesco Borrelli$^{2}$, J. Christian Gerdes$^{1}$% <-this % stops a space
\thanks{*This work was supported by the Hyundai Center of Excellence}% <-this % stops a space
\thanks{$^{1}$Dept. of Mechanical Engineering, Stanford University. Nitin Kapania is also a visiting scholar at UC Berkeley.}%
\thanks{$^{2}$Dept. of Mechanical Engineering, UC Berkeley.}%
}

@@

&\\
 2. Efficiency & a. Average speed: Minimize \\ 
        & deviation from speed of traffic \\  
        & b. Wait for pedestrian crossing \\
        & event to materialize before \\
        & yielding. \\

        & \\
 3. Smoothness & a. Low acceleration: Nominal \\ 
 			  & brake and acceleration limits \\
 			  & of 2 $\mathrm{m/s^2}$ \\

@@

\If {$state = HARD\hspace{1mm}BRAKING$}
	\State $v_{des} = \mathrm{getDesiredSpeed}(d, v)$
	\State $a = -\frac{v^2}{2d} + k_s(v - v_{des})$ 	
	\If {$\textbf{not} \hspace{1mm} \mathrm{inCrosswalk}(x_p)$} \State $state \leftarrow DRIVING$

@@

% \EndIf
\If {$state = SPEED\hspace{1mm}UP$}
	\State $a = a_\mathrm{cmf}$ 	
	\If {$\textbf{not} \hspace{1mm} \mathrm{inCrosswalk}(x_p) \vee d < 0$} \State $state \leftarrow DRIVING$
